---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# parrot

<!-- badges: start -->
<!-- badges: end -->

Arguably, the biggest drawback in R is the inability to use party parrots.
`parrot` tries to close that gap by providing a way to insert party parrots into the RStudio viewer and in documents.
`parrot` provides functions to download gifs from <https://cultofthepartyparrot.com/> and use them.

## Installation

You can install the development version of parrot from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("christopherkenny/parrot")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# load the library
library(parrot)

# set the option to use the cache
options(parrot.use_cache = TRUE)

# download the parrots
parrot_download()

# party
party('parrot')
```
